---
title: "Methamphetmine Use and Driving Behaviour"
subtitle: "Predictors of dangerous driving behaviour in Methamphetamine users"
author: "Aaron Mackay"
institute: "Swinburne University Centre for Human Psychopharmacology"
date: "Updated: `r Sys.Date()`"
output: xaringan::moon_reader
  
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Source the objects
```
# Looking at the data
This is text

``` r
code <- "test"
```
This is __bold.__

This is _italics_

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


---
## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
